Draft

### 2020-10-15 Final.Rmd
fixed vix trace plot date error

fsr10plot <- fsr10 %>% ggplot(aes(x=Date)) +
  geom_line(aes(y = CLS10,color = "CLS10"),size=0.25)+
  geom_line(aes(y = CLS20,color = "CLS20"),size=0.25)+
  geom_line(aes(y = MLE,color = "MLE"),size=0.25)+
  geom_line(aes(y = CRPS,color = "CRPS"),size=0.25)+
  labs(x="Year",y="Average Scores",color="legend")+
  #ggtitle("Figure 12: S&P500 Score traces-lower tail")+
  scale_x_date(date_breaks = "years",date_labels = "%y")+
  scale_color_manual(values = color1)+
  annotate(geom = 'text',x=as.Date("2008-09-18"),y=0.15,label="Global Financial Crisis",color="darkred")+
  annotate(geom = 'text',x=as.Date("2020-03-11"),y=0.15,label="COVID-19",color="darkred",size = 2)+
  theme_clean()

@@

fsr10 <- fsr10 %>% mutate(Date = vix$Date[1001:6000])

@@

fsr90 <- fsr90 %>% mutate(Date = vix$Date[1001:6000])

>>>>

fsr10plot <- fsr10 %>% ggplot(aes(x=Date)) +
  geom_line(aes(y = CLS10,color = "CLS10"),size=0.3,linetype = "dashed")+
  geom_line(aes(y = CLS20,color = "CLS20"),size=0.5,linetype = "dotted")+
  geom_line(aes(y = MLE,color = "MLE"),size=0.3,linetype = "solid")+
  geom_line(aes(y = CRPS,color = "CRPS"),size=0.3, linetype = "longdash")+
  labs(x="Year",y="Average Scores",color="legend")+
  #ggtitle("Figure 12: S&P500 Score traces-lower tail")+
  scale_x_date(date_breaks = "years",date_labels = "%y")+
  scale_color_manual(values = color1)+
  annotate(geom = 'text',x=as.Date("2008-09-18"),y=0.15,label="Global Financial Crisis",color="darkred")+
  annotate(geom = 'text',x=as.Date("2020-03-11"),y=0.15,label="COVID-19",color="darkred",size = 2)+
  theme_clean()

@@

fsr10 <- fsr10 %>% mutate(Date = logvix$Date[1001:6000])

@@

fsr90 <- fsr90 %>% mutate(Date = logvix$Date[1001:6000])
